%-------------------------
% Resume in Latex
% Author : Dejoe John
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Dejoe John} \\ \vspace{1pt}
    \small 929-977-9929 $|$ \href{mailto:dejoejohn@gmail.com}{{dejoejohn@gmail.com}} $|$ 
    \href{https://linkedin.com/in/dejoe}{\underline{linkedin.com/in/dejoe}} $|$
    \href{https://github.com/dej0e}{\underline{github.com/dej0e}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Technical Specialist}{Sep. 2020 -- Aug 2023}
      {Infrrd Inc.}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Spearheaded Infrrd’s SaaS offering - Intelligent Document Processing (IDP) backend platform migration from legacy monolith to redesigned state-of-the-art microservice tech stack }
        \resumeItem{Overhauled data extraction logic used in the backend of Infrrd’s IDP offering to accurately extract up to 95\% successfully. }
        \resumeItem{Led two technology teams for distinct service clients and successfully delivered projects on time.}
          \begin{itemize} 
            \item \textit{homegenius Inc} - Mobile-first team of 8 Software Engineers and 2 QA Engineers.
            \item \textit{ZAGENO GmbH} - Remote Python team of 4 Software Engineers and 2 QA Engineers.  
          \end{itemize}
        \resumeItem{Mentor newer engineers on the team to make sure there is alignment with strategic goals.}
        \resumeItem{Liaised between different tech-stack stakeholders to make project development seamless.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Software Engineer}{Oct. 2018 -- Sep. 2020}
      {Infrrd Inc.}{Bengaluru, India}
      \resumeItemListStart
      \resumeItem{Architected and led the development of a highly scalable real estate mobile application for iOS and Android platforms for Radian Group Inc.}
      \resumeItem{Re-engineered an existing native mobile application to a hybrid application, cutting development costs by 45\%.}
      \resumeItem{Bagged a mobile project from Nokia after competing in their Acronym Camera Recognition on Open Ecosystem Network.}
      \resumeItem{Streamlined processes using Agile Methodologies, sprint planning, and execution to make developers more efficient and productive.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Sep. 2016 -- Oct. 2018}
      {Infrrd Inc.}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Programmed new features and maintained existing modules in a real estate mobile application.}
        \resumeItem{Engineered Android SDK for Infrrd’s erstwhile offering - \textit{Gimlet} (Data Extraction from Invoices).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {New Jersey Institute of Technology}{Newark, NJ}
    {Master of Science in Computer Science}{Sep. 2018 -- Current}
  \resumeSubheading
    {Sardar Vallabhbhai National Institute of Technology, Surat (NIT Surat)}{Surat, India}
    {Bachelor of Technology in Computer Engineering }{July 2012 -- May 2016}
\resumeSubHeadingListEnd
%----------------------------------------

%-----------LEADERSHIP AND ACTIVITIES-----------
\section{Leadership and Activities}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Google Developer Group, NIT Surat} $|$ \emph{Organising Member}}{Feb. 2015}
          \resumeItemListStart
            \resumeItem{Conducted technical and design workshops for young engineers with pioneers in the industry}
            \resumeItem{Coordinated with and organized sponsors for events.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{InOut - India’s Biggest Community Hackathon} $|$ \emph{Founding Organiser}}{Oct. 2015}
          \resumeItemListStart
            \resumeItem{Led the Public Relations team responsible for print and social media engagement.}
            \resumeItem{Conducted the initial iterations of InOut at NIT Surat.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Kotlin, Swift, Python, C/C++, Objective C, SQL (Postgres, MySQL, SQLite), NOSQL (MongoDB), HTML/CSS} \\
     \textbf{Frameworks}{: Spring Boot, Hibernate, Flask, JUnit, Material-UI, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, Google Cloud Platform, Android Studio, XCode, VS Code, PyCharm, IntelliJ } \\
    }}
 \end{itemize}
%-------------------------------------------

\end{document}
